The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-18 Presentation/slides.qmd
update slides - multiple formats and test images

---
title: "The Role of Variability in Learning Generalization"
format: 
  revealjs:
    theme: moon #white
    slideNumber: true
    center: true
    chalkboard: true
author: Thomas Gorman
institute: Indiana University
---

@@

@@

@@

@@

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
  clean-revealjs:
    #theme: moon #white
    output-ext: slide.html
    slideNumber: true
    center: true
    chalkboard: true
  pptx:
    incremental: true
author:
  - name: Thomas Gorman
    orcid: 0000-0000-0000-0000
    affiliations: Indiana University
---

@@

![](assets/fig-toy-model1-1-1.png)

@@

![](assets/methodsFig1.png)

@@

::: {.content-visible unless-format="markdown"}
```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 7.0
//| fig-height: 2.5
//| fig-responsive: false
//| echo: false  
///| eval: !expr out_type 
/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled]

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }

  Test2 -> Test3
}
```
:::

@@

## Project 2 - ALM

![](assets/fig-alm-diagram-1-1.png)
